Lucy.js: Client-Side Indexes for Fast Full-Text Searching

### 2014-12-11 paper/paper.tex
Added some perf text

@@

@@

@@

@@

\begin{figure}
   \includegraphics[scale=.53]{query-times}
  \caption{Comparison of query times for various queries with different result set sizes (left to right: smaller to larger) between our three main types of indexes and sequential search (the only way to search strings that indexedDB offers). }
\end{figure}

>>>>

We can see that if we discard children and child-less nodes, our index basically becomes a simple inverted index with no stemming. However, traversing the subtree for prefix searches also makes it function like a prefix trie, hence the name Hybrid (prefix/suffix) trie.

@@

\subsubsection{Asynchronous depth-first search}

Since IndexedDB is multi-threaded, every step of a single transaction is asynchronous. This brings several challenges to writing transactions that are not present in most other DBMS', where concurrency conundrums only arise in the context of multiple concurrent transactions.

Even something as simple as a depth-first search on our trie subtree becomes nontrivial when asynchronicity is added in the mix. Individual statements (reads or writes) are atomic, but reads and writes can be interleaved in any possible way (unless special care is taken to enforce a specific interleaving, at the cost of parallelism).

For the DFS case, we maintain a counter of pending paths that we pass by reference to the recursive method responsible for traversing the tree, decrement it by 1 when we reach a leaf and increment it by 1 when we encounter a subtree with more than one elements. When the counter becomes zero at a leaf, we conclude the search.

@@

\subsection{Data set}

For the performance comparisons in this section we used a CSV dataset of a one million tweet sample originally intended for sentiment analysis\footnote{http://help.sentiment140.com/for-students}.

We first removed unneeded information such as sentiment flags to reduce the size of the dataset, as we are only interested in textual content. We then wrote an ad-hoc Python script to select a random subset and convert it to JSON, which is what the generic IndexedDB importer we wrote expected.

After several tests with different sample sizes, we settled for about 5\% of the data (44771 tweets), since our target browser (Google Chrome) was having difficulty with larger datasets.

@@

For our 44771 tweets dataset, it took (average of 3 index creations) 3 minutes and 21 seconds to build the inverted index, 47 minutes and 24 seconds to build the prefix trie, 48 minutes and 12 seconds to build the suffix trie and 2 minutes and 53 seconds to build the hybrid prefix trie (we did not measure

@@

We tried four different queries with different result set sizes (from 25 to 2398) on index type, as well as plain sequential search, which is the only type of string search that IndexedDB offers out of the box. The results can be seen in Figure~\ref{querytimes}.

While all of our indexes have comparable performance, they outperform sequential search by several orders of magnitude. Sequential search for all four of our queries seems to be taking close to 3 seconds, whereas our index-optimized queries take only about 10-100ms.

\begin{figure}
   \includegraphics[scale=.53]{query-times}
  \caption{Comparison of query times for various queries with different result set sizes (left to right: smaller to larger) between our three main types of indexes and sequential search (the only way to search strings that indexedDB offers). }
  \label{querytimes}
\end{figure}
